Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies

### 2017-03-11 First_np_Paper/first_np_paper.tex
Finished squashing comments, sending out draft for next edits...

\comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe}

@@

\comment{Use your energy-angle figure from Lisken above to estimate these numbers. You can point to the figure in the text if you'd like.}

@@

\comment{Truncate sig figs here - Note that the systematic uncertainty you calculated in the previous paragraph will provide a natural limit on the number of significant figures you quote for the energy window.}

@@

Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  \textcolor{red}{2.7645 MeV +0.151/-0.219} neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley. The cross sections were measured with a  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}. The measured values of \textcolor{red}{XXXX and YYYY}, respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements. In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast (e.g., $\approx$2.45 MeV) neutrons, rather than from \enquote{room return} thermal neutrons. The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.

\comment{Truncate sig figs above, fill in values, use correct fast neutron energy above}

@@

>>>>

\comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe - no change in results, purely cosmetic.}

@@

\comment{Can someone use the energy-angle figure from Lisken above (or another tool) to estimate these numbers?
% You can point to the figure in the text if you'd like.
}

@@

\comment{Truncate sig figs here - Note that the systematic uncertainty  calculated in the previous paragraph will provide a natural limit on the number of significant figures to quote for the energy window.}

@@

Using activation methods on thin foils, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections were measured for  \textcolor{red}{2.7645 MeV +0.151/-0.219} neutrons produced using the High Flux Neutron Generator (HFNG) at UC Berkeley. The cross sections were measured with a  5\% uncertainty relative to the well-known \ce{^{115}In}(n,n')\ce{^{115m}In} and \ce{^{113}In}(n,n')\ce{^{113m}In} fast neutron cross sections \cite{Capote2012,zsolnay2012technical}. The measured values of  26.262 $\pm$  0.822 mb and  46.415 $\pm$ 1.720 mb (relative to \ce{^{113}In})  or 49.315 $\pm$ 2.567 mb (relative to \ce{^{115}In}), respectively, are consistent with earlier experimental data and theoretical models, but have smaller uncertainties than previous measurements. In addition, the results for the production of \ce{^{116}In} via the \ce{^{115}In}(n,$\gamma$) reaction was shown to be consistent with activation from the capture of fast \textcolor{red}{(e.g., $\approx$2.45 MeV)} neutrons, rather than from \enquote{room return} thermal neutrons. The use of DD neutron generators can be an efficient method for the measurement of low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies.

\comment{Truncate sig figs above, use correct fast neutron energy above}

@@

\comment{Can someone estimate the energy of the corner foils?}
